\name{}: machine learning over interaction networks and ontology-based background knowledge predicts drug--target interactions

### 2021-07-12 paper/main.tex
.

\todo{TODO}Most of novel predictions made by \name{} are for antineoplastic
agents targeting proteins belonging to the Zinc finger, LIM-type
family ({\tt IPR001781}).

@@

As the target-based predictive power of \name{} improves significantly over other methods, we utilized our model to predict novel drug classes for protein families. We therefore collected the 2nd level ATC (Anatomical Therapeutic Chemical) groups for each drug and all InterPro \cite{Interpro2020} top-level families for each protein. Utilizing the STITCH interactions, we followed a protein split within each InterPro family by predicting over all available drugs. We eventually normalized the number of novel interactions per class by the amount of proteins within the respective family. A heatmap showing the results of this analysis can be found in Supplementary figure 5. \dots \todo{Roberts class analysis}.

>>>>

@@

As the target-based predictive power of \name{} improves significantly
over other methods, we utilized our model to predict novel drug
classes for protein families. We therefore collected the 2nd level ATC
(Anatomical Therapeutic Chemical) groups for each drug and all
InterPro \cite{Interpro2020} top-level families for each
protein. Utilizing the STITCH interactions, we followed a protein
split within each InterPro family by predicting over all available
drugs. We eventually normalized the number of novel interactions per
class by the amount of proteins within the respective family. A
heatmap showing the results of this analysis can be found in
Supplementary Figure 5. \dots \todo{Roberts class analysis}.

Most of novel predictions made by \name{} are for antineoplastic
agents targeting proteins belonging to the Zinc finger, LIM-type
family ({\tt IPR001781}).
